---
title: "Poisson Regression and Applications"
author: "Adam Dawson, Sarah Onstad-Hawes, and Asare Buahin"
date: "12/11/2019"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```




##  Introduction: Main Project Questions

- What is the Poisson Regression and what are it's applications?

- Using the Poisson Regression, can we find significant relationships within our data set.


## Introduction: Our Data Set




 - "Contact with Medical Doctors"
 
    - Cross-Sectional data collected in North Carolina between 1977-78
 
    - Examines 20186 observations of individuals
 
      - Randomly selected subset of 2000 observations for ease of computation
    
    - Collected from RAND Health Insurance Experiment (RHIE), which is the longest and largest socially controlled experiment regarding medical care (Price, D. 2002)
    
    - Our Response Variable of interest is mdu, which captures the number of times an individual visited a medical health profession during the study
    
    - Data Set also contains 14 other variables of interest
      

## Introduction: Our Research Question

- How is the number of doctor visits impacted by various factors in an individual's life?

  - Specifically, we want see how one's age, sex, income, physical limitations, and present diseases influence their ability to seek out medical care.  
  
- Use the Poisson Regression to model the data and see what relationships, if any, exist in between our variables.  


## Methodology: The Poisson Distribution

- A probability function which is especially useful for count data
    - $Y$ is a variable with discrete outcomes ($0,1,2,...$) where high counts for $Y$ are rare
    - $f(Y) = \frac{\mu^{Y}*e^{-\mu}}{Y!}$
    - $E[Y] = \mu$
    - $P(Y = y) = \frac{\mu^{y}*e^{-\mu}}{y!}$
    - $\mu$ also sometimes noted as $\lambda$
    
## Methodology: Necessary Conditions for the Poisson Distribution

- The Mean and Variance of Y are the equal
  - $E[Y] = V[Y] = \mu$
  
- Independence
  - An event A occuring does not impact event B from occuring
  
- Probabilities are porportional to time
  - A is twice as likely to occur in two-hour window than in one hour.
  
- Each observation is recorder over the same fixed period of time.

- Data Set is not overloaded with zero counts. 

## Methodology: The Poisson Regression

- Poisson Regression finds estimates for the linear equation relating the log of a response variable to predictors.
  - $log(\hat{\mu}) = \beta_{0} + \beta_{1}X_{1} + \beta_{2}X_{2} + ... + \beta_{p}X_{p}$
  - $\hat{\mu} = e^{\beta_{0} + \beta_{1}X_{1} + \beta_{2}X_{2} + ... + \beta_{p}X_{p}}$
-  Allows us to see how a marginal change in our predictor variable impacts the estimated count of our variable.  
- Coefficients found using the Maximum Likelihood Estimate process

- Coefficients evalued for statisical significance using z-statistic and corresponding p-value

- We can use R glm function where we indicate the family to be "poisson" in order to obtain our fitted equation and coefficient estimates. 

## Results and Conclusions: An Introduction to our Data:

```{r, message = FALSE, warning = FALSE}
library(ggplot2)
library(dplyr)
library(tibble)
library(here)
library(Stat2Data)
library(knitr)
library(leaps)
library(GGally)

Doctor <- read.csv(here("", "DoctorContacts.csv"))
Doctor <- as_tibble(Doctor)

set.seed(1)
Doc_sample <- Doctor[sample(1:nrow(Doctor), 2000,
   replace=FALSE),]

Doctor_Summary <- Doc_sample %>%
            	summarize(count = n(), st.dev = round(sd(mdu),2),
                      	sample_mean = round(mean(mdu),2), med = round(median(mdu), 2),
                        	min = min(mdu), max = max(mdu))
kable(Doctor_Summary)
```

- $\mu$ = 2.87, $\sigma^{2}$ = 4.56

  - Over-disperion present

## Results and Conclusions: Our Data

```{r, message =  FALSE, warning= FALSE, fig.height = 2, fig.width = 3, fig.cap= "Count of an Individual's Doctors Visits in a Year"}
p <- ggplot(data = Doc_sample)

p + geom_histogram(mapping = aes(x = mdu), bins = 50 )
```


- Histogram shows a distribution skewed to the right
  - A high number of 0 counts in our data set

## Discussion and Critiques: Model Assumptions

- We have good reason to question a few necessary assumptions of the Poisson Distribution in regards to our data set

- Mean and Variance are not equal $E[Y] = 2.8$ and $V[Y] = 4.5$
  - Over-dispersion, which could indicate that we should use a different model

- We have a large number of observations for which the count is 0

- Consider using a different model to fit to our data
  - Zero-Inflated Poisson Regression
    - accounts for large number of 0 counts in data set
  - Zero-Inflated Negative Binomial Regression
    - helps with both larger number of 0s and over-dispersion


## Discussion and Critiques: Inference

- With our data being so significant (perhaps abnormally), we were unsure of our ability to use the fitted equation with any confidence

- With a high number of possible predictors, we could have ommitted some very significant variables from the regression, which could be vital in understanding what impacts utilization of healthcare.

- Data set is from the 1970s
  - Comprehensive, but outdated
  - If using data to enact policy shifts or structural changes, our data analysis might not be "in touch" enough with the current climate of health care. 
 
 - Data is collected from N.C. only, which limits the scope in which we can make inferences.
  - Perhaps some cultural/societal impacts in N.C. region impacted our data
  - US healthcare system unique, so inferences at most apply only to US.
  
 
## Conclusion

- Poisson Regression is useful for analyzing count data, but it is crucial to check the data set and see that conditions are met prior to analysis and inference

- Having a large sample size is helpful, but also must be aware of how that potentially impacts analysis.

- Working on real world data is tough and messy. Takes a lot more time and careful thought
  - No exact, clear path for analysis
- "One step forward, two steps back"

## References

https://stats.idre.ucla.edu/r/dae/poisson-regression/
https://stats.idre.ucla.edu/stata/output/poisson-regression/
https://stats.idre.ucla.edu/r/dae/zip/
https://www.sciencedirect.com/science/article/pii/S0167629602000085
https://www.dataquest.io/blog/tutorial-poisson-regression-in-r/#:~:targetText=Poisson%20Regression%20models%20are%20best,where%20the%20outcomes%20are%20counts.&targetText=Poisson%20Regression%20helps%20us%20analyze,the%20count%20or%20a%20rate).


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

