---
title: "Poisson Regression and Applications"
author: "Adam Dawson, Sarah Onstad-Hawes, and Asare Buahin"
date: "12/11/2019"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



## Introduction

### Applying the Poisson Regression

####  Main Project Questions

- What is the Poisson Regression and what are it's applications?

- Using the Poisson Regression, can we find significant relationships within our data set.


## Introduction Continued

### Our Data Set and Research Question

 - "Contact with Medical Doctors"
 -- Cross-Sectional data collected in North Carolina between 1977-78
 -- Examines 20186 observations of individuals
 --- Randomly selected subset of 2000 observations for ease of computation




## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

