---
title: "Final"
author: "AD, SO-H, AB"
date: "11/21/2019"
output: pdf_document
---


```{r, message = FALSE, warning = FALSE}
library(ggplot2)
library(dplyr)
library(tibble)
library(here)
library(Stat2Data)
library(knitr)
library(leaps)
library(GGally)

Doctor <- read.csv(here("", "DoctorContacts.csv"))
Doctor <- as_tibble(Doctor)
Doctor

Doc_sample <- Doctor[sample(1:nrow(Doctor), 2000,
   replace=FALSE),]

Doc_sample
Doctor_Summary <- Doctor %>%
            	summarize(count = n(), st.dev = round(sd(mdu),2),
                      	sample_mean = round(mean(mdu),2), med = round(median(mdu), 2),
                        	min = min(mdu), max = max(mdu))
Doctor_Summary
```

\vspace{0.5cm}
```{r}
p <- ggplot(data = Doc_sample)

p + geom_histogram(mapping = aes(x = mdu), bins = 50 )

model <- glm(mdu~physlim+ndisease+linc+age+sex, Doc_sample, family=poisson)
regmod1<-glm(mdu~physlim, Doc_sample, family=poisson)
regmod2<-glm(mdu~ndisease, Doc_sample, family=poisson)
regmod3<-glm(mdu~linc, Doc_sample, family=poisson)
regmod4<-glm(mdu~age, Doc_sample, family=poisson)
regmod5<-glm(mdu~sex, Doc_sample, family=poisson)
p.physlim <- summary(regmod1)$coefficients[2,4]
p.disease <- summary(regmod2)$coefficients[2,4]
p.linc <- summary(regmod3)$coefficients[2,4]
p.age <- summary(regmod4)$coefficients[2,4]
p.sex <- summary(regmod5)$coefficients[2,4]
rbind(p.physlim, p.disease, p.linc,p.age,p.sex)
```

ndisease has the lowest p value of the 5 variables
```{r}
regmod11<-glm(mdu~ndisease+physlim, Doc_sample, family=poisson)
regmod12<-glm(mdu~ndisease+linc, Doc_sample, family=poisson)
regmod13<-glm(mdu~ndisease+age, Doc_sample, family=poisson)
regmod14<-glm(mdu~ndisease+sex, Doc_sample, family=poisson)
p.dp <- summary(regmod11)$coefficients[2,4]
p.dli <- summary(regmod12)$coefficients[2,4]
p.da <- summary(regmod13)$coefficients[2,4]
p.ds <- summary(regmod14)$coefficients[2,4]
rbind(p.dp, p.dli, p.da,p.ds)
```
```{r}
regmod21<-glm(mdu~ndisease+linc+physlim, Doc_sample, family=poisson)
regmod22<-glm(mdu~ndisease+linc+age, Doc_sample, family=poisson)
regmod23<-glm(mdu~ndisease+linc+sex, Doc_sample, family=poisson)
p.dlp <- summary(regmod21)$coefficients[2,4]
p.dla <- summary(regmod22)$coefficients[2,4]
p.dls <- summary(regmod23)$coefficients[2,4]
rbind(p.dlp, p.dla, p.dls)
```
```{r}
regmod31<-glm(mdu~ndisease+linc+sex+physlim, Doc_sample, family=poisson)
regmod32<-glm(mdu~ndisease+linc+sex+age, Doc_sample, family=poisson)
p.dlsp <- summary(regmod21)$coefficients[2,4]
p.dlsa <- summary(regmod22)$coefficients[2,4]
rbind(p.dlsp, p.dlsa)
```
```{r}
regmod41<-glm(mdu~ndisease+linc+sex+physlim+age, Doc_sample, family=poisson)
p.dlspa <- summary(regmod22)$coefficients[2,4]
rbind(p.dlspa)
```
Therefore, we can add all the 5 variables considered to our model since they all have significant p values. We will use a stepwise regression to confirm that this is the best model
```{r}
full <- lm(mdu ~ physlim+ndisease+linc+age+sex, data = Doc_sample)
null <- lm(mdu ~ 1, data = Doc_sample)
#We can perform forward selection using the command:
step(null, scope=list(lower=null, upper=full), direction="forward")
```

```{r}
Probof4ormore = ppois(4,lambda=2.86, lower.tail=FALSE)
Probof4ormore
```
The code above gives us the probability that a person will go to the doctor's office 4 or more times in a year. We can edit the lower.tail component of this code to give us the probablity that a person will go to the doctor's office 4 or less times in a year
```{r}
Probof4orless = ppois(4,lambda=2.86, lower.tail=TRUE)
Probof4orless
```

```{r}
summary(model)
```
From our knowledge on Poisson Distribution, we can write out the regression model like so
$$log(MDU) = -1.02+1.44PhysLim + 0.09NDisease + 0.248LInc + 0.03Age - 0.311Male$$
Which is equivalent to 
$$MDU = e^{-1.02+1.44PhysLim + 0.09NDisease + 0.248LInc + 0.03Age - 0.311Male}$$
What we can see from this model:
- Men visit the doctor's office less than women do.

