---
title: "Poisson Regression and Applications"
author: "Adam Dawson, Sarah Onstad-Hawes, and Asare Buahin"
date: "12/11/2019"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```




##  Introduction: Main Project Questions

- What is the Poisson Regression and what are it's applications?

- Using the Poisson Regression, can we find significant relationships within our data set.


## Introduction: Our Data Set




 - "Contact with Medical Doctors"
 
    - Cross-Sectional data collected in North Carolina between 1977-78
 
    - Examines 20186 observations of individuals
 
      - Randomly selected subset of 2000 observations for ease of computation
    
    - Collected from RAND Health Insurance Experiment (RHIE), which is the longest and largest socially controlled experiment regarding medical care (Price, D. 2002)
    
    - Our Response Variable of interest is mdu, which captures the number of times an individual visited a medical health profession during the study
    
    - Data Set also contains 14 other variables of interest
      

## Introduction: Our Research Question

- How is the number of doctor visits impacted by various factors in an individual's life?

  - Specifically, we want see how one's age, sex, income, physical limitations, and present diseases influence their ability to seek out medical care.  
  
- Use the Poisson Regression to model the data and see what relationships, if any, exist in between our variables.  


## Methodology: The Poisson Distribution

- A probability function which is especially useful for count data
    - $Y$ is a variable with discrete outcomes ($0,1,2,...$) where high counts for $Y$ are rare
    - $$ f(Y) = \frac{\mu^{Y}*e^{-\mu}}{Y!} $$
    - $$ E[Y] = \mu $$
    
## Methodology: Necessary Conditions for the Poisson Distribution

- The Mean and Variance of Y are the equal
  - $E[Y] = V[Y] = \mu$
  
- Independence
  - An event A occuring does not impact event B from occuring
  
- Probabilities are porportional to time
  - A is twice as likely to occur in two-hour window than in one hour. 


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

